---
title: "From metawebs to regional and local"
author: "L.A.S."
output: html_document
editor_options: 
  chunk_output_type: console
---

* This is to determine the general structure of all empirical networks and comparison against a random null model Erdos-Renyi (ER), not included in the manuscript.
* Topological roles for the empirical networks is calculated here

## Setup

- **I run the analysis chunk by chunk, not the whole Rmd** 

- So I set `eval=TRUE` or `eval=FALSE` to run a particular chunk or I run it interactively 

```{r setup, eval=TRUE,echo=TRUE,message=FALSE }

if(file.exists(".RData")) load(".RData")

source("R/network_fun.r")

require(igraph)
require(dplyr)
require(stringr)
require(cowplot)
if( require(meweasmo) == FALSE)
  install_github("lsaravia/meweasmo")
if( require(multiweb) == FALSE)
  install_github("lsaravia/multiweb")

require(tidyverse)
```

# Read the Antarctic Metawebs files with New Weddell without False Basal species 2020/10/08 

```{r readAnt, eval=TRUE,echo=FALSE,message=FALSE }
#
dn <- list.files("Data",pattern = "^[MWP].*\\.dat$")
dn <- paste0("Data/", dn)
dn <- dn[c(2,3,1)]
ig_list <- readNetwork(dn,edgeListFormat=2)
names(ig_list) <- c("Ant_Potter","Ant_Weddell","Ant_Meta")

```


# QSS -  Modularity - SW - Analysis - Antarctic metaweb  

```{r ModularityAnalysisAnt08, eval=FALSE,echo=F,message=FALSE,warning=TRUE}

# simulations_ER <- tibble()
# websTbl <- tibble()

simulations_ER <- simulations_ER %>% filter(!grepl("Ant",Network))
websTbl <- websTbl %>% filter(!grepl("Ant",Network))
lapply(names(ig_list), function(fw){
    res <- compare_with_ER(ig_list[[fw]], fw,1000)
    simulations_ER <<- bind_rows(simulations_ER, res$sim)
    websTbl <<- bind_rows(websTbl, res$su)
})

rm(sim,dtot,dtot1,f)

save.image()

require(pander)
panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')

pandoc.table((websTbl %>% dplyr::select(Network,Size,Links,Connectance,PathLength,Clustering,SWness,SWnessCI,Q,zQ,Qlow,Qhigh,mTI,zTI,TIlow,TIhigh,Modularity,zMO,MOlow,MOhigh) %>% mutate_if(is.numeric, round, digits=4)))

knitr::kable(websTbl %>% dplyr::select(Network,Size,Links,Connectance,PathLength,Clustering,SWness,SWnessCI,Q,zQ,Qlow,Qhigh,mTI,zTI,TIlow,TIhigh,Modularity,zMO,MOlow,MOhigh) %>% mutate_if(is.numeric, round, digits=4))


knitr::kable(websTbl %>% dplyr::select(Metaweb,Network,Size,Links,Connectance,Q,mTI,Modularity,MEing) %>% mutate_if(is.numeric, round, digits=4) %>% arrange(Metaweb,Links))

knitr::kable(websTbl %>% dplyr::select(Metaweb,Network,Size,Links,Connectance,Q,mTI,Modularity,MEing) %>% mutate_if(is.numeric, round, digits=4) %>% arrange(Metaweb,Connectance))

# 100 simulations for modularity

loc_list <- ig_list[names(ig_list) %in% "Ant_Meta" == FALSE]
names(loc_list)

webs_modul <- tibble()
w_modul <- lapply(1:100, function(x){
  calc_modularity(loc_list,8)  %>% mutate(Network=names(loc_list))
})
webs_modul <- bind_rows(w_modul) %>% group_by(Network) %>% summarise(sdMod=sd(Modularity), Modularity=mean(Modularity) )

rm(w_modul,loc_list)
save.image()

```


# Motif Analysis - Antarctic

```{r MotifAnalysisMetaWeb, eval=FALSE,echo=F,message=T,warning=T}
#
# Motif
#
# motif_ER <- tibble()
# all_motif_freq <- tibble()

motif_ER <- motif_ER %>% filter(!grepl("Ant",Network))
all_motif_freq <- all_motif_freq %>% filter(!grepl("Ant",Network))

lapply(names(ig_list), function(fw){
    res <- calc_compare_motif(ig_list[[fw]], fw,1000)
    motif_ER <<- bind_rows(motif_ER, res$moter)
    all_motif_freq <<- bind_rows(all_motif_freq, res$fallm)
})

save.image()

require(pander)
panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')

motif_ER <- motif_ER %>% dplyr::select(Network, everything())

pandoc.table(t(motif_ER %>% mutate_if(is.numeric, round, digits=4)))
knitr::kable(motif_ER %>% mutate_if(is.numeric, round, digits=4))
```

# Analisis of motif frequency change across networks

Pag 616 The R book

```{r MotifAnalysisMetaWebAcross, eval=FALSE,echo=F,message=T,warning=T}
require(dplyr)
#
# Build a dataframe with the relevant motifs
# 
pFM<- all_motif_freq %>% filter(grepl("Ant",Network)) %>% group_by(Network) %>% dplyr::select(X4:X6,X9) %>% rename(EC=X4,AC=X5,TT=X6,OM=X9) %>% mutate(Tot=sum(EC,AC,TT,OM)) %>% ungroup()

require(tidyr)

pFM1 <- pFM %>% mutate(EC=EC/Tot,AC=AC/Tot,TT=TT/Tot, OM=OM/Tot) %>% dplyr::select(Network:OM) %>%gather(motif,count,EC:OM)
levels(pFM1$Network) <- c("Potter Cove","Weddell Sea","Meta-web")
require(ggplot2)
gP1 <- ggplot(pFM1,aes(x=Network,y=count,fill=motif)) + geom_bar(stat="identity") + 
  scale_fill_brewer(palette = "RdYlGn", breaks=c("EC","AC","TT","OM"), name="", labels=c("Exploitative\ncompetition", "Apparent\ncompetition", "Tri-trophic\nchain","Omnivory")) + 
  xlab("") + ylab("Proportion") + theme_bw() + theme(legend.position="bottom")
#ggsave("Figures/MotifProportionByNetwork.png",width=6,height=6,units="in",dpi=600)

#
# Test it using poisson glm (only the interaction counts )
#
pFM1 <- pFM %>%  dplyr::select(Network:OM) %>%gather(motif,count,EC:OM)

model1 <- glm(count~Network*motif,poisson, data=pFM1)
summary(model1)
model2 <- glm(count~Network+motif,poisson, data=pFM1)
summary(model2)

anova(model1,model2,test="Chi")

#
# Pearson Chi-squared independence 
#

x <- all_motif_freq %>% filter(grepl("Ant",Network))%>% dplyr::select(X4:X6,X9) %>% rename(EC=X4,AC=X5,TT=X6,OM=X9)
x <- as.matrix(x)
rownames(x) <- c("Potter Cove","Weddell Sea","Meta-web")
require(RColorBrewer)
colnet <- brewer.pal(4,"Paired")[c(1,4)]
png("Figures/Ant_NetworkByMotifFreq.png",width=7,height=6,units="in",res=600)
par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(2, 2, 0, 2))
colnames(x) <- c("Exploitative\ncompetition", "Apparent\ncompetition", "Tri-trophic\nchain","Omnivory")
assocplot(t(x),col=colnet)
dev.off()
#require(vcd)
#assoc(x, main = "Relation Network and motif", shade = TRUE)

chisq.test(x,simulate.p.value = T, B=10000)
# spineplot(x)

#         Pearson's Chi-squared test with simulated p-value (based on 10000
#         replicates)
# 
# data:  x
# X-squared = 8730.5, df = NA, p-value = 9.999e-05

```
 
# Topological Roles of empirical Networks


@Kortsch2015

The role is described by two parameters: (i) the standardized within-module degree z and (ii) the among-module
connectivity participation coefficient PC. The z-score reflects how well a species is connected to other species inside the module relative to other species within its own module. The PC parameter estimates the distribution of a species’ connections across the modules.


```{r topologicalRoles, eval=TRUE,echo=F,message=FALSE,warning=T}

source("R/network_fun.r")

require(igraph)
require(dplyr)
require(stringr)

#
# Add the modulos object to a vector  
#
set.seed(123)
mod_by_red <- vector(mode="list", length=length(ig_list))
require(future.apply)
plan(multiprocess)
future_lapply( seq_len(length(ig_list)), function(i){
  modulos<-cluster_spinglass(ig_list[[i]])
  mod_by_red[[i]] <<- modulos
})
plan(sequential)


# topo_roles <- tibble()
# hub_conn <- tibble()
topo_roles <- topo_roles %>% filter(!grepl("Ant",Network))
hub_conn <- hub_conn %>% filter(!grepl("Ant",Network))

lapply(names(ig_list), function(fw){
    topo_roles <<- bind_rows(topo_roles,incremental_topoRoles(ig_list[[fw]], fw))
    i <- which( names(ig_list)==fw)
    hub_conn <<- bind_rows(hub_conn, plot_topological_roles(filter(topo_roles,Network==fw),ig_list[[fw]],mod_by_red[[i]]) %>% mutate(Network=fw))

})


# unique(topo_roles$Network)
# topo_roles <- topo_roles %>% mutate(Network = factor(Network), Network=fct_recode(Network, Ant_Potter = "Potter Cove", Ant_Weddell = "Weddell Sea",Ant_Meta = "Meta-web" ))  

save.image()

```

# Antarctic Plot of topological roles with confidence interval 

```{r Ant_topologicalRolesCI, eval=FALSE,echo=F,message=T,warning=T}

#
#

require(ggplot2)
unique(topo_roles$Network)
tp <- topo_roles %>% filter(grepl("Ant_", Network))
tp$Network <- factor(tp$Network, levels = c("Ant_Potter","Ant_Weddell","Ant_Meta")) 
levels(tp$Network)= c("Potter Cove","Weddell Sea","Meta")

g <- ggplot(tp, aes(x=among_module_conn,y=within_module_degree,colour=Network),shape=21) +  theme_bw() + geom_point()+ 
	geom_errorbar(aes(ymin=wtmLowCI, ymax=wtmHiCI),width=0.0,alpha=0.5) +
  geom_errorbarh(aes(xmin = amcLowCI, xmax = amcHiCI),height=0.0,alpha=0.5) + 
  ylab("Within module degree") + xlab("Among module connectivity") +
	scale_colour_brewer(palette="Dark2",name="Network") + theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90, hjust = 0))

g + geom_hline(aes(yintercept=2.5),linetype = 2) + geom_vline(aes(xintercept=0.625),linetype = 2) +facet_wrap( ~Network)

#ggsave("Figures/Ant_TopoRolesCI_ByNetwork.png",width=7,height=5,units="in",dpi=600)

#
# Add network area to the table with network info
# 
websTbl$Area <- c(6.8,3.5e6,34.8e6)

```


# Generate dataframe with topological roles species names trophic level and degree 

```{r checkTopoRolesTLmod, eval=FALSE,echo=F,message=T,warning=T}
require(dplyr)

tRD <- tibble()
lapply(names(ig_list), function(fw){
    tRD <<-  bind_rows(tRD, getTopoRolesTLdegree(ig_list[[fw]], fw, hub_conn))
})
topoRolesDegree <- tRD

topoRolesDegree %>% group_by(Network,type) %>% summarise(n=n())

# Generate table of more connected topological roles
#
require(pander)
panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')

# Change names of networks
# topoRolesDegree$Network <- factor(topoRolesDegree$Network, levels=c("Ant_Potter", "Ant_Weddell","Ant_Meta"))
# levels(topoRolesDegree$Network) <- c("Potter","Weddell","Meta-web")

pandoc.table(topoRolesDegree %>% filter(type=="hubcon" | type=="modhub" ) %>% arrange(type,Network,trophLevel) %>%  dplyr::select(type,Network,name,preys,predators,trophLevel) %>% mutate_if(is.numeric, round, digits=2))
write_csv(topoRolesDegree,"Data/Ant_topoRoles_degree.csv")
# 
#

topoRolesDegree %>% mutate(basal=(round(trophLevel,2)<=1)) %>% group_by(type,Network,basal) %>% summarise(n=n())

rm(tRD)

save.image()

```


## Read the Islands data set and make topological analysis

```{r readIslands, eval=FALSE,echo=TRUE,message=FALSE }

require(readr)

#
# Extract Islands from GATEWAy database
#
ga <- readr::read_csv("~/Dropbox/Projects/MetaWebsAssembly/Data/283_2_FoodWebDataBase_2018_12_10.csv",col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")

fw_name <- ga %>% filter(grepl("Piechnik",link.citation )) %>% distinct(foodweb.name)                
Have_df <- ga %>% filter(grepl("Piechnik",link.citation )) %>% dplyr::select(con.taxonomy,con.taxonomy.level,res.taxonomy,res.taxonomy,foodweb.name)
require(igraph)
dtot1 <- as.matrix(Have_df %>% dplyr::select(res.taxonomy,con.taxonomy))
have1  <- graph_from_edgelist(dtot1, directed  = T)
have1 <- igraph::simplify(have1,remove.loops = FALSE)                            ## !! Delete all duplicated links 


df_list <- Have_df %>% group_split(foodweb.name)
ig_list <- lapply(df_list, function(fw) {
  d1 <- as.matrix(fw %>% dplyr::select(res.taxonomy,con.taxonomy))
  graph_from_edgelist(d1, directed  = T)
})
names(ig_list) <- paste0("Isl_",fw_name$foodweb.name)
ig_list <- c(ig_list, list(Isl_Meta=have1))

multiweb::calc_topological_indices(ig_list)
```


# QSS -  Modularity - SW - Analysis - Florida Islands metaweb  

```{r qssIslands, eval=FALSE,echo=TRUE,message=FALSE }

lapply(names(ig_list), function(fw){
    res <- compare_with_ER(ig_list[[fw]], fw,1000)
    simulations_ER <<- bind_rows(simulations_ER, res$sim)
    websTbl <<- bind_rows(websTbl, res$su)
})

rm(sim,dtot,dtot1,f,ga,have1,Have_df)

save.image()

require(pander)
panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')

pandoc.table(t(websTbl %>% filter(grepl("Isl_", Network)) %>%
                                  dplyr::select(Network,Size,Links,Connectance,PathLength,Clustering,SWness,SWnessCI,Q,zQ,Qlow,Qhigh,mTI,zTI,TIlow,TIhigh,Modularity,zMO,MOlow,MOhigh) %>% mutate_if(is.numeric, round, digits=4)))


# 100 simulations for modularity

loc_list <- ig_list[names(ig_list) %in% "Isl_Meta" == FALSE]
names(loc_list)

w_modul <- lapply(1:100, function(x){
  calc_modularity(loc_list,8)  %>% mutate(Network=names(loc_list))
})
webs_modul <- bind_rows(w_modul) %>% group_by(Network) %>% summarise(sdMod=sd(Modularity), Modularity=mean(Modularity) ) %>% bind_rows(webs_modul)

rm(w_modul,loc_list)
save.image()


```


# Motif Analysis - Florida Islands

```{r MotifIslands, eval=FALSE,echo=F,message=T,warning=T}
#
# Motif
#

lapply(names(ig_list), function(fw){
    res <- calc_compare_motif(ig_list[[fw]], fw,1000)
    motif_ER <<- bind_rows(motif_ER, res$moter)
    all_motif_freq <<- bind_rows(all_motif_freq, res$fallm)
})

save.image()

require(pander)
panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')

motif_ER <- motif_ER %>% dplyr::select(Network, everything())

save.image()

pandoc.table(t(motif_ER %>% filter(grepl("Isl_", Network)) %>% mutate_if(is.numeric, round, digits=4)))

#
# Build a dataframe with the relevant motifs
# 
pFM<- all_motif_freq %>% filter(grepl("Isl_", Network)) %>% group_by(Network) %>% dplyr::select(X4:X6,X9) %>% rename(EC=X4,AC=X5,TT=X6,OM=X9) %>% mutate(Tot=sum(EC,AC,TT,OM)) %>% ungroup()

require(tidyr)

pFM1 <- pFM %>% mutate(EC=EC/Tot,AC=AC/Tot,TT=TT/Tot, OM=OM/Tot) %>% dplyr::select(Network:OM) %>%gather(motif,count,EC:OM)
#levels(pFM1$Network) <- c("Potter Cove","Weddell Sea","Meta-web")
require(ggplot2)
gP1 <- ggplot(pFM1,aes(x=Network,y=count,fill=motif)) + geom_bar(stat="identity") + 
  scale_fill_brewer(palette = "RdYlGn", breaks=c("EC","AC","TT","OM"), name="", labels=c("Exploitative\ncompetition", "Apparent\ncompetition", "Tri-trophic\nchain","Omnivory")) + 
  xlab("") + ylab("Proportion") + theme_bw() + theme(legend.position="bottom")
#ggsave("Figures/Isl_MotifProportionByNetwork.png",width=6,height=8,units="in",dpi=600)


#
# Pearson Chi-squared independence 
#

x <- all_motif_freq %>% filter(grepl("Isl_", Network)) %>% dplyr::select(Network,X4:X6,X9) %>% rename(EC=X4,AC=X5,TT=X6,OM=X9)
rnames <- x$Network 
rnames <- c("E1","E2","E3","E7","E9","Islands\nMeta")
x <- as.matrix(x[,2:5])
rownames(x) <- rnames
require(RColorBrewer)
colnet <- brewer.pal(4,"Paired")[c(1,4)]
png("Figures/Isl_NetworkByMotifFreq.png",width=6,height=6,units="in",res=600)
par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(2, 2, 0, 2))
colnames(x) <- c("Exploitative\ncompetition", "Apparent\ncompetition", "Tri-trophic\nchain","Omnivory")
assocplot(t(x),col=colnet)
dev.off()

chisq.test(x,simulate.p.value = T, B=10000)

# 	Pearson's Chi-squared test with simulated p-value (based on 10000 replicates)
# 
# data:  x
# X-squared = 478.84, df = NA, p-value = 9.999e-05


```

# Islands Topological Roles

```{r IslandsTopologicalRoles, eval=FALSE,echo=F,message=FALSE,warning=T}

#
# Add the modulos object to a vector  
#
set.seed(123)
mod_by_red <- vector(mode="list", length=length(ig_list))
require(future.apply)
plan(multiprocess)
future_lapply( seq_len(length(ig_list)), function(i){
  modulos<-cluster_spinglass(ig_list[[i]])
  mod_by_red[[i]] <<- modulos
})
plan(sequential)

topo_roles$Network <- as.character(topo_roles$Network)

lapply(names(ig_list), function(fw){
    topo_roles <<- bind_rows(topo_roles,incremental_topoRoles(ig_list[[fw]], fw))
    i <- which( names(ig_list)==fw)
    hub_conn <<- bind_rows(hub_conn, plot_topological_roles(filter(topo_roles,Network==fw),ig_list[[fw]],mod_by_red[[i]]) %>% mutate(Network=fw))

})

save.image()

```

#  Islands Plot of topological roles with confidence interval

```{r IsltopologicalRolesCI, eval=FALSE,echo=F,message=T,warning=T}

#
tp <- topo_roles %>% filter(grepl("Isl_", Network)) %>% mutate(Network=factor(Network))
levels(tp$Network) <-gsub('^(.{7})(.{6})(.*)$', '\\1\\\n\\2 \\3', str_sub(levels(tp$Network),5))

gsub('^([a-z])([A-z])(.*)$', '\\1\\\n\\2 \\3', str_sub(levels(tp$Network),5))

g <- ggplot(tp, aes(x=among_module_conn,y=within_module_degree,colour=Network),shape=21) +  theme_bw() + geom_point()+ 
	geom_errorbar(aes(ymin=wtmLowCI, ymax=wtmHiCI),width=0.0,alpha=0.5) +
  geom_errorbarh(aes(xmin = amcLowCI, xmax = amcHiCI),height=0.0,alpha=0.5) + 
  ylab("Within module degree") + xlab("Among module connectivity") +
	scale_colour_brewer(palette="Dark2",name="Network") + theme(legend.position="none") +  theme(axis.text.x = element_text(angle = 90, hjust = 0))

g + geom_hline(aes(yintercept=2.5),linetype = 2) + geom_vline(aes(xintercept=0.625),linetype = 2) +facet_wrap( ~Network)


#
# Plot topological roles by module and trophic level
#
plotTopoRolesByTLByMod("Isl_FloridaIslandE1","",topoFrame=hub_conn,redl=ig_list[["Isl_FloridaIslandE1"]])
plotTopoRolesByTLByMod("Isl_FloridaIslandE2","",topoFrame=hub_conn,redl=ig_list[["Isl_FloridaIslandE2"]])
plotTopoRolesByTLByMod("Isl_Meta","",topoFrame=hub_conn,redl=ig_list[["Isl_Meta"]])


#
#
#
require(dplyr)

tRD <- tibble()
lapply(names(ig_list), function(fw){
    tRD <<-  bind_rows(tRD, getTopoRolesTLdegree(ig_list[[fw]], fw, hub_conn))
})

topoRolesDegree <- bind_rows(tRD,topoRolesDegree)

topoRolesDegree %>% group_by(Network,type) %>% summarise(n=n())

topoRolesDegree$Network <- factor(topoRolesDegree$Network)
levels(topoRolesDegree$Network) <- c("Florida\nIsland E1","Florida\nIsland E2","Florida\nIsland E3","Florida\nIsland E7", "Florida\nIsland E9","Islands\nMetaweb","Antarctic\nMetaweb","Potter","Weddell"    )
# Generate table of more connected topological roles
#
require(pander)
panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')

#
# Change names of networks
#
pandoc.table(topoRolesDegree %>% filter(type=="hubcon" | type=="modhub" ) %>% arrange(type,Network,trophLevel) %>%  dplyr::select(type,Network,name,preys,predators,trophLevel) %>% mutate_if(is.numeric, round, digits=2))

# 
#

topoRolesDegree %>% mutate(basal=(round(trophLevel,2)<=1)) %>% group_by(type,Network,basal) %>% summarise(n=n())

rm(tRD,topoRoles)

save.image()


```

## Read the 50 Lakes Havens Food Webs


```{r readLakes, eval=FALSE,echo=TRUE,message=FALSE }

require(tidyverse)

#
# Extract Weddell Sea from GATEWAy database
#
ga <- readr::read_csv("~/Dropbox/Projects/MetaWebsAssembly/Data/283_2_FoodWebDataBase_2018_12_10.csv",col_types = "icccccccccccccddddddccccccccddddddcddccddciicc")

fw_name <- ga %>% filter(grepl("Havens",link.citation )) %>% distinct(foodweb.name)                
Have_df <- ga %>% filter(grepl("Havens",link.citation )) %>% dplyr::select(con.taxonomy,con.taxonomy.level,res.taxonomy,res.taxonomy,foodweb.name)
require(igraph)
dtot1 <- as.matrix(Have_df %>% dplyr::select(res.taxonomy,con.taxonomy))
have1  <- graph_from_edgelist(dtot1, directed  = T)

df_list <- Have_df %>% group_split(foodweb.name)
ig_list <- lapply(df_list, function(fw) {
  d1 <- as.matrix(fw %>% dplyr::select(res.taxonomy,con.taxonomy))
  graph_from_edgelist(d1, directed  = T)
})

names(ig_list) <- paste0("Lak_",str_replace_all(fw_name$foodweb.name," ","_"))
ig_list <- c(ig_list, list(Lak_Meta=have1))

```

# QSS -  Modularity - SW - Analysis - Lakes metaweb  

```{r qssLakes, eval=FALSE,echo=TRUE,message=FALSE }

lapply(names(ig_list), function(fw){
    res <- compare_with_ER(ig_list[[fw]], fw,1000)
    simulations_ER <<- bind_rows(simulations_ER, res$sim)
    websTbl <<- bind_rows(websTbl, res$su)
})

rm(sim,dtot,dtot1,f,ga,have1,Have_df,df_list,df1,tp,x,pFM,pFM1)

save.image()

require(pander)
panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')

pandoc.table(t(websTbl %>% filter(grepl("Lak_", Network)) %>%
                                  dplyr::select(Network,Size,Links,Connectance,PathLength,Clustering,SWness,SWnessCI,Q,zQ,Qlow,Qhigh,mTI,zTI,TIlow,TIhigh,Modularity,zMO,MOlow,MOhigh) %>% mutate_if(is.numeric, round, digits=4)))

# Modularity 

loc_list <- ig_list[names(ig_list) %in% "Lak_Meta" == FALSE]
names(loc_list)

require(future.apply)
plan(multisession)

w_modul <- lapply(1:100, function(x){
  mm <- future_lapply(loc_list, function(ln){
    tibble(Modularity= calc_modularity_unconnected(ln)$modularity)
  },future.seed=TRUE)
  mm <- bind_rows(mm)  %>% mutate(Network=names(loc_list))
})
webs_modul <- bind_rows(w_modul) %>% group_by(Network) %>% summarise(sdMod=sd(Modularity), Modularity=mean(Modularity) ) %>% bind_rows(webs_modul)

plan(sequential)
rm(w_modul,loc_list)
websTbl <- inner_join(websTbl %>% rename(Modularity_old=Modularity),webs_modul,by=c("Network"))

save.image()

```

# Motif Analysis - Lakes

```{r MotifIsLakes, eval=FALSE,echo=F,message=T,warning=T}
#
# Motif
#

lapply(names(ig_list), function(fw){
    res <- calc_compare_motif(ig_list[[fw]], fw,1000)
    motif_ER <<- bind_rows(motif_ER, res$moter)
    all_motif_freq <<- bind_rows(all_motif_freq, res$fallm)
})

save.image()

require(pander)
panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')

motif_ER <- motif_ER %>% dplyr::select(Network, everything())

save.image()
require(pander)
pandoc.table(t(motif_ER %>% filter(grepl("Lak_", Network)) %>% mutate_if(is.numeric, round, digits=4)))

#
# Build a dataframe with the relevant motifs
# 
pFM<- all_motif_freq %>% filter(grepl("Lak_", Network)) %>% group_by(Network) %>% dplyr::select(X4:X6,X9) %>% rename(EC=X4,AC=X5,TT=X6,OM=X9) %>% mutate(Tot=sum(EC,AC,TT,OM)) %>% ungroup()

require(tidyr)

pFM1 <- pFM %>% mutate(EC=EC/Tot,AC=AC/Tot,TT=TT/Tot, OM=OM/Tot) %>% dplyr::select(Network:OM) %>%gather(motif,count,EC:OM)
#levels(pFM1$Network) <- c("Potter Cove","Weddell Sea","Meta-web")
require(ggplot2)
gP1 <- ggplot(pFM1,aes(x=Network,y=count,fill=motif)) + geom_bar(stat="identity") + 
  scale_fill_brewer(palette = "RdYlGn", breaks=c("EC","AC","TT","OM"), name="", labels=c("Exploitative\ncompetition", "Apparent\ncompetition", "Tri-trophic\nchain","Omnivory")) + 
  xlab("") + ylab("Proportion") + theme_bw() + theme(legend.position="bottom") + theme(axis.text.x = element_text(angle = 90, hjust=0))
#ggsave("Figures/MotifProportionByNetwork.png",width=6,height=6,units="in",dpi=600)


#
# Pearson Chi-squared independence 
#

x <- all_motif_freq %>% filter(grepl("Lak_", Network)) %>% dplyr::select(Network,X4:X6,X9) %>% rename(EC=X4,AC=X5,TT=X6,OM=X9)
rnames <- x$Network
x <- as.matrix(x[,2:5])
rownames(x) <- rnames
require(RColorBrewer)
colnet <- brewer.pal(11,"RdYlGn")[c(1,11)]
#png("Figures/NetworkByMotifFreq.png",width=6,height=6,units="in",res=600)
par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(2, 2, 0, 2))
colnames(x) <- c("Exploitative\ncompetition", "Apparent\ncompetition", "Tri-trophic\nchain","Omnivory")
assocplot(t(x),col=colnet)
#dev.off()

chisq.test(x,simulate.p.value = T, B=10000)

# Pearson's Chi-squared test with simulated p-value (based on 10000 replicates)
# 
# data:  x
# X-squared = 5503.2, df = NA, p-value = 9.999e-05


```


# Lakes Topological Roles

```{r LakesTopologicalRoles, eval=FALSE,echo=F,message=FALSE,warning=T}


#
# Add the modulos object to a vector  
#
set.seed(123)
# mod_by_red <- vector(mode="list", length=length(ig_list))
# require(future.apply)
# plan(multiprocess)
# future_lapply( seq_len(length(ig_list)), function(i){
#   modulos<-calc_modularity_unconnected(ig_list[[i]])
#   mod_by_red[[i]] <<- modulos
# })
# plan(sequential)

topo_roles$Network <- as.character(topo_roles$Network)

lapply(names(ig_list), function(fw){
    topo_roles <<- bind_rows(topo_roles,incremental_topoRoles(ig_list[[fw]], fw))
    i <- which( names(ig_list)==fw)
    hub_conn <<- bind_rows(hub_conn, classify_topological_roles(filter(topo_roles,Network==fw),ig_list[[fw]]) %>% mutate(Network=fw))

})

topo_roles %>% group_by(Network) %>% summarise(n=n())

save.image()

```

# Antarctic Topological Roles proportions test and plot

```{r Ant_topologicalRolesTestPlot, eval=FALSE,echo=F,message=T,warning=T}

#
#
unique(hub_conn$Network)
tbl <- hub_conn %>% filter(grepl("Ant_", Network))
tbl <- table(tbl$Network,tbl$type)


tbl1 <- tbl[c(1,3,2),] 

chisq.test(tbl,simulate.p.value = TRUE, B=10000)
# 	Pearson's Chi-squared test with simulated p-value (based on 10000 replicates)
# 
# data:  tbl
# X-squared = 65.148, df = NA, p-value = 9.999e-05

require(ggplot2)
require(scales)
df1 <- data.frame(tbl1)
names(df1) <- c("Network","Rol","count")
df1 <- filter(df1,count!=0)
df1 <- df1 %>% group_by(Network) %>% mutate(total=sum(count),Freq=count/total)
levels(df1$Network) <- c("Metaweb","Weddell Sea","Potter Cove")


gP2 <- ggplot(df1,aes(x=forcats::fct_relevel(Network, "Potter Cove","Weddell Sea"),y=Freq,fill=Rol)) + geom_bar(stat="identity") + 
  scale_fill_brewer(palette = "Paired",name="") + 
  xlab("") + ylab("") + theme_bw() + theme(legend.position="bottom") + coord_flip()
#ggsave("Figures/TopoRolesProportionByNetwork.png",width=6,height=6,units="in",dpi=600)


# Plot motif frequency 
# 
#
pFM<- all_motif_freq  %>% filter(grepl("Ant_", Network)) %>% group_by(Network) %>% dplyr::select(X4:X6,X9) %>% rename(EC=X4,AC=X5,TT=X6,OM=X9) %>% mutate(Tot=sum(EC,AC,TT,OM)) %>% ungroup()
require(tidyr)
pFM1 <- pFM %>% mutate(EC=EC/Tot,AC=AC/Tot,TT=TT/Tot, OM=OM/Tot) %>% dplyr::select(Network:OM) %>%gather(motif,count,EC:OM)
pFM1$Network <- factor(pFM1$Network)
levels(pFM1$Network) <- c("Metaweb","Potter Cove","Weddell Sea")
require(ggplot2)
gP1 <- ggplot(pFM1,aes(x=forcats::fct_relevel(Network, "Potter Cove","Weddell Sea"),y=count,fill=motif)) + geom_bar(stat="identity") + 
  scale_fill_brewer(palette = "Paired", breaks=c("EC","AC","TT","OM"), name="", labels=c("Exploitative\ncompetition", "Apparent\ncompetition", "Tri-trophic\nchain","Omnivo-\nry")) + 
  xlab("") + ylab("") + theme_bw() + theme(legend.position="bottom") + coord_flip()



gP1 <- gP1 +  theme(legend.key.width = unit(.5, "cm"))
gP2 <- gP2 +  theme(legend.key.width = unit(.5, "cm"))

require(cowplot)
gP3 <- plot_grid(gP1,gP2,labels = c("A","B"),align = "h")
save_plot("Figures/Ant_PropMotif_Roles.png",gP3,base_width=8,base_height=5,dpi=600)

```

# Islands Plots Topological Roles proportions test and plot

```{r IsltopologicalRolesTestPlot, eval=FALSE,echo=F,message=T,warning=T}

#
#
unique(hub_conn$Network)
tbl <- hub_conn %>% filter(grepl("Isl_", Network))
tbl <- table(tbl$Network,tbl$type)

tbl1 <- tbl[c(1,3,2),] 

chisq.test(tbl,simulate.p.value = TRUE, B=10000)
# 	Pearson's Chi-squared test with simulated p-value (based on 10000 replicates)
# 
# data:  tbl
# X-squared = 516.15, df = NA, p-value = 9.999e-05

require(ggplot2)
require(scales)
df1 <- data.frame(tbl)
names(df1) <- c("Network","Rol","count")
df1 <- filter(df1,count!=0)
df1 <- df1 %>% group_by(Network) %>% mutate(total=sum(count),Freq=count/total)
levels(df1$Network) <- gsub('^(.{7})(.{6})(.*)$', '\\1\\ \\2 \\3', str_sub(levels(df1$Network),5))
df1$Network <- fct_recode(df1$Network, Metaweb="Meta")
levels(df1$Network) <- str_replace_all( levels(df1$Network), "Florida", "")

#
# Create a new variable to plot in order of hubcon+modhub+modcon 
require(tidyverse)
df2 <- df1 %>% pivot_wider(-c(count,total),names_from=Rol,values_from = Freq,values_fill = list(Freq=0)) %>% 
  mutate(orden = hubcon+modhub+modcon)
df1 <- df1 %>% full_join(df2 %>% select(Network,orden)) %>% ungroup() %>% mutate(Network=fct_reorder(Network,orden))

gP5 <- ggplot(df1,aes(x=Network,y=Freq,fill=Rol)) + geom_bar(stat="identity") + 
  scale_fill_brewer(palette = "Paired",name="") + 
  xlab("") + ylab("") + theme_bw() + theme(legend.position="bottom") + coord_flip()
#ggsave("Figures/TopoRolesProportionByNetwork.png",width=6,height=6,units="in",dpi=600)

# Plot motif frequency 
# 
#
pFM<- all_motif_freq %>% filter(grepl("Isl_", Network)) %>% group_by(Network) %>% dplyr::select(X4:X6,X9) %>% rename(EC=X4,AC=X5,TT=X6,OM=X9) %>% mutate(Tot=sum(EC,AC,TT,OM)) %>% ungroup() %>% mutate(Network=factor(Network))
levels(pFM$Network) <-gsub('^(.{7})(.{6})(.*)$', '\\1\\ \\2 \\3', str_sub(levels(pFM$Network),5))
pFM$Network <- fct_recode(pFM$Network, Metaweb="Meta")
levels(pFM$Network) <- str_replace_all( levels(pFM$Network), "Florida", "")
 
pFM <- full_join(pFM, df2 %>% select(Network,orden))

pFM1 <- pFM %>% mutate(Network=fct_reorder(Network, orden),EC=EC/Tot,AC=AC/Tot,TT=TT/Tot, OM=OM/Tot) %>% dplyr::select(Network:OM) %>%gather(motif,count,EC:OM)

require(ggplot2)
gP4 <- ggplot(pFM1,aes(x=Network,y=count,fill=motif)) + geom_bar(stat="identity") + 
  scale_fill_brewer(palette = "Paired", breaks=c("EC","AC","TT","OM"), name="", labels=c("Exploitative\ncompetition", "Apparent\ncompetition", "Tri-trophic\nchain","Omnivo-\nry")) + 
  xlab("") + ylab("") + theme_bw() + theme(legend.position="bottom") + coord_flip()

gP4 <- gP4 +  theme(legend.key.width = unit(.5, "cm"))
gP5 <- gP5 +  theme(legend.key.width = unit(.5, "cm"))

require(cowplot)
gP6 <- plot_grid(gP4,gP5,labels = c("A","B"),align = "h")
save_plot("Figures/Isl_PropMotif_Roles.png",gP6,base_width=8,base_height=5,dpi=600)
```

# Lakes Plots Topological Roles proportions test and plot

```{r LaktopologicalRolesTestPlot, eval=FALSE,echo=F,message=T,warning=T}
require(ggplot2)
#
#
unique(hub_conn$Network)
tbl <- hub_conn %>% filter(grepl("Lak_", Network))
tbl <- table(tbl$Network,tbl$type)

tbl1 <- tbl[c(1,3,2),] 

chisq.test(tbl,simulate.p.value = TRUE, B=10000)

# 	Pearson's Chi-squared test with simulated p-value (based on 10000 replicates)
# 
# data:  tbl
# X-squared = 1414.1, df = NA, p-value = 9.999e-05

require(ggplot2)
require(scales)
df1 <- data.frame(tbl)
names(df1) <- c("Network","Rol","count")
df1 <- filter(df1,count!=0)
df1 <- df1 %>% group_by(Network) %>% mutate(total=sum(count),Freq=count/total)
levels(df1$Network) <- str_replace_all( str_sub(levels(df1$Network),5), "_", " ")
df1$Network <- fct_recode(df1$Network, Metaweb="Meta")

#
# Create a new variable to plot the lakes in order of hubcon 
require(tidyverse)
df2 <- df1 %>% pivot_wider(-c(count,total),names_from=Rol,values_from = Freq,values_fill = list(Freq=0)) %>% 
  mutate(orden = hubcon+modhub+modcon)
df1 <- df1 %>% full_join(df2 %>% select(Network,orden)) %>% ungroup() %>% mutate(Network=fct_reorder(Network,orden))
#forcats::fct_relevel(Network, "Meta", after = Inf)

(gP8 <- ggplot(df1,aes(x=Network  ,y=Freq,fill=Rol)) + 
    geom_bar(stat="identity") + 
  scale_fill_brewer(palette = "Paired",name="") + 
  xlab("") + ylab("") + theme_bw() + theme(legend.position="bottom") + coord_flip())
#ggsave("Figures/Lak_TopoRolesProportionByNetwork.png",width=8,height=6,units="in",dpi=600)

# Plot motif frequency 
# 
#
pFM<- all_motif_freq %>% filter(grepl("Lak_", Network)) %>% group_by(Network) %>% dplyr::select(X4:X6,X9) %>% rename(EC=X4,AC=X5,TT=X6,OM=X9) %>% mutate(Tot=sum(EC,AC,TT,OM)) %>% ungroup() %>% mutate(Network=factor(Network))
levels(pFM$Network) <- str_replace_all( str_sub(levels(pFM$Network),5), "_", " ")
pFM$Network <- fct_recode(pFM$Network, Metaweb="Meta")

pFM <- full_join(pFM, df2 %>% select(Network,orden))
pFM1 <- pFM %>% mutate(Network=fct_reorder(Network, orden), EC=EC/Tot,AC=AC/Tot,TT=TT/Tot, OM=OM/Tot) %>% dplyr::select(Network:OM) %>%gather(motif,count,EC:OM)

gP7 <- ggplot(pFM1,aes(x=Network,y=count,fill=motif)) + geom_bar(stat="identity") + 
  scale_fill_brewer(palette = "Paired", breaks=c("EC","AC","TT","OM"), name="", labels=c("Exploitative\ncompetition", "Apparent\ncompetition", "Tri-trophic\nchain","Omnivo-\nry")) + 
  xlab("") + ylab("") + theme_bw() + theme(legend.position="bottom") + coord_flip()

gP7 <- gP7 +  theme(legend.key.width = unit(.5, "cm"))
gP8 <- gP8 +  theme(legend.key.width = unit(.5, "cm"))

require(cowplot)
gP9 <- plot_grid(gP7 + theme(legend.text=element_text(size=7)),
                 gP8 + theme(axis.text.y=element_blank(),legend.text=element_text(size=7)),
                 labels = c("A","B"),align = "h",rel_widths = c(1.3,1))
save_plot("Figures/Lak_PropMotif_Roles.png",gP9,base_width=8,base_height=5,dpi=600)

# !!! FALTA ELMINAR LAS LEYENDAS DEL EJE Y EN LOS PLTS DE LA DERECHA

gP10 <- plot_grid(gP1 + theme(legend.position="none",),
                  gP2 + theme(legend.position="none",axis.text.y=element_blank()),
                  gP4 + theme(legend.position="none"),
                  gP5 + theme(legend.position="none",axis.text.y=element_blank()),
                  gP7 + theme(legend.text=element_text(size=7)),
                  gP8 + theme(axis.text.y=element_blank(),legend.text=element_text(size=7)), 
                  align = "v",
                  ncol = 2,
                  labels = c("A","B"),
                  rel_heights = c(1,1.3,6),
                  rel_widths = c(1,1))

gP10
save_plot("Figures/Total_PropMotif_Roles.png",gP10,base_width=8,base_height=6,dpi=600)


#
# Plots of metrics 
#
websTbl <- websTbl %>% select(Network, everything()) %>% mutate(Metaweb=str_sub(Network,1,3), ismeta = grepl("Meta",Network)) 

require(ggrepel)
gP1 <- ggplot(websTbl, aes(x=Size,y=MEing,color=ismeta)) + geom_point() +scale_color_brewer(palette = "Paired", ,guide=NULL) + facet_wrap( ~Metaweb, scale="free_x") + theme_bw() + xlab(NULL)
gP2 <-ggplot(websTbl, aes(x=Size,y=Modularity,color=ismeta)) + geom_point() +scale_color_brewer(palette = "Paired", ,guide=NULL) + facet_wrap( ~Metaweb, scale="free_x") + theme_bw() + xlab(NULL)
gP3 <- ggplot(websTbl, aes(x=Size,y=SWness,color=ismeta)) + geom_point() +scale_color_brewer(palette = "Paired", ,guide=NULL) + facet_wrap( ~Metaweb, scale="free_x") + theme_bw() + xlab(NULL)
gP4 <- ggplot(websTbl, aes(x=Size,y=TLmean,color=ismeta)) + geom_point() +scale_color_brewer(palette = "Paired", ,guide=NULL) + facet_wrap( ~Metaweb, scale="free_x") + theme_bw()
gP6 <- ggplot(websTbl, aes(x=Size,y=Q,color=ismeta)) + geom_point() +scale_color_brewer(palette = "Paired", ,guide=NULL) + facet_wrap( ~Metaweb, scale="free_x") + theme_bw()
gP7 <- ggplot(websTbl, aes(x=Size,y=LD,color=ismeta)) + geom_point() +scale_color_brewer(palette = "Paired", ,guide=NULL) + facet_wrap( ~Metaweb, scale="free_x") + theme_bw()

gP5 <- plot_grid(gP1 + theme(axis.text.x=element_blank()),
                  gP2 + theme(axis.text.x=element_blank()),
                  gP3 + theme(axis.text.x=element_blank()),
                  gP4 , 
                  align = "v",
                  ncol = 1)

save_plot("Figures/Total_Metrics_byMeta.png",gP5,base_width=6,base_height=7,dpi=600)


gP1 <- ggplot(websTbl, aes(x=Size,y=MEing,color=ismeta)) + geom_point() +scale_color_brewer(palette = "Paired", ,guide=NULL) + facet_wrap( ~Metaweb, scale="free_x") + theme_bw() + xlab(NULL) + ylab("Asymmetric MEing")
gP2 <- ggplot(websTbl, aes(x=Size,y=MEing1,color=ismeta)) + geom_point() +scale_color_brewer(palette = "Paired", ,guide=NULL) + facet_wrap( ~Metaweb, scale="free_x") + theme_bw() + xlab("Size") + ylab("Symmetric MEing")
gP3 <- ggplot(websTbl, aes(x=Size,y=Q,color=ismeta)) + geom_point() +scale_color_brewer(palette = "Paired", ,guide=NULL) + facet_wrap( ~Metaweb, scale="free_x") + theme_bw() + xlab(NULL)

gP5 <- plot_grid(gP3 + theme(axis.text.x=element_blank()),
  gP1 + theme(axis.text.x=element_blank()),
                  gP2 , 
                  align = "v",
                  ncol = 1)

save_plot("Figures/MEing_Metrics_byMeta.png",gP5,base_width=6,base_height=7,dpi=600)

```
